Global patterns of forest autotrophic carbon fluxes

### 2020-02-13 manuscript/manuscript draft.Rmd
Table 1: remove H1.1.alt and H1.2
#48

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "Summary of hypotheses, corresponding specific predictions, and results. Direction of significant relationships is indicated by '+' and '-', and  shape is summarized as linear (L), concave up (CU), and concave down (CD). 'n.s.' indicates that the relationship is not signficant.") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do FACFs vary with latitude?", 1, 3, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q2. How do FACFs vary with MAT and MAP?", 4, 6, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q3. How are FACFs related to climate variables, other than MAT and MAP?", 7, 9, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence FACFs?", 10, 13, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do FACFs vary with climate?", 14, 17, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", " ", " ", "Forest autotrophic carbon fluxes (FACF)" = 9, " ")) %>%
  #column_spec(1, width = "15cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3:13, width = "1.8cm") %>%
  kableExtra::landscape()
```

>>>>

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "Summary of hypotheses, corresponding specific predictions, and results. Direction of significant relationships is indicated by '+' and '-', and  shape is summarized as linear (L), concave up (CU), and concave down (CD). 'n.s.' indicates that the relationship is not signficant.") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do FACFs vary with latitude?", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Q2. How do FACFs vary with MAT and MAP?", 2, 4, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q3. How are FACFs related to climate variables, other than MAT and MAP?", 5, 7, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence FACFs?", 8, 11, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do FACFs vary with climate?", 12, 15, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", " ", " ", "Forest autotrophic carbon fluxes (FACF)" = 9, " ")) %>%
  #column_spec(1, width = "15cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3:13, width = "1.8cm") %>%
  kableExtra::landscape()
```
